\section*{Safety Strategy Internship}
\addcontentsline{toc}{section}{Safety Strategy Internship}
\subsection*{At a Glance}
\begin{itemize}
    \item \textbf{Salary:} \$5,500–7,500/month
    \item \textbf{Location:} \textbf{Foster City, CA}
    \item \textbf{Duration:} January 8 to April 8
    \item \textbf{Type:} Internship, Full-time
\end{itemize}

\subsection*{Qualifications}
\begin{itemize}
    \item \textbf{Experience with data, data mining, or data analysis.}
    \item \textbf{Experience with vehicle safety and safety standards.}
    \item Currently pursuing a Bachelor’s or Master’s degree in engineering, computer science, or data science.
\end{itemize}

\subsection*{About Zoox}
Detailed information about Zoox, focusing on its innovation and mission in autonomous vehicle technology.

\subsection*{Improvement Notes and Project Suggestions}
\textbf{Develop Data Analysis Skills:} Enhance expertise in handling and interpreting safety-related data.\\
\textbf{Project Idea:} Implement a safety data analysis project using public datasets to demonstrate your analytical skills.

\subsection*{Resume Tailoring and Project Strategy for Safety Strategy Internship}
\textbf{Resume Tips:}
\begin{itemize}
    \item Highlight any data analysis or related projects, especially those involving Python or similar tools.
    \item Emphasize coursework and skills in data science and engineering.
\end{itemize}

\textbf{Project Idea:}
Develop a data-centric project focusing on vehicle safety, using statistical tools to analyze and present your findings.

