\section*{Requirement Analysis and Planning for Fleet Management Dashboard}
\addcontentsline{toc}{section}{Analysis and Planning}

\subsection*{Project Overview}
The Fleet Management Dashboard is designed to offer real-time insights, tracking, and analytics to enhance the operational efficiency of fleet management. It serves as an integral tool for fleet managers and coordinators to monitor and optimize their fleet operations effectively.

\subsection*{User Stories}
\begin{itemize}
    \item \textbf{Fleet Manager:} As a fleet manager, I want to view the real-time location of all vehicles to optimize routing and ensure timely deliveries.
    \item \textbf{Maintenance Coordinator:} As a maintenance coordinator, I want to receive automated alerts for vehicle maintenance needs to proactively address any issues and minimize downtime.
\end{itemize}

\subsection*{Identifying Key Features}
\begin{itemize}
    \item Real-time vehicle tracking and status updates.
    \item Maintenance scheduling and alert notifications.
    \item Analytical reports and dashboards for performance assessment.
    \item User role-based access control to ensure data security and relevancy.
\end{itemize}

\subsection*{Defining the Scope}
The initial phase will focus on developing the core functionalities that provide the most value, such as the tracking system and maintenance alerts. Subsequent iterations will introduce analytics and customized user experiences based on the role.

\subsection*{Technology Stack}
\begin{itemize}
    \item \textbf{Frontend:} Next.js to leverage server-side rendering and enhance SEO while providing a robust framework for our React application.
    \item \textbf{Backend:} (If applicable) Node.js with Express.js for creating RESTful APIs that interact with our database and serve the frontend.
    \item \textbf{Database:} A choice between PostgreSQL and MongoDB, depending on the data structure and requirements identified during the planning phase.
\end{itemize}

\subsection*{Planning for Scalability and Security}
It's crucial to plan for scalability from the outset, ensuring that the dashboard can handle increasing amounts of data and user load. Security measures, including data encryption and secure API endpoints, will be integral from the initial development phase.

