\section*{Full Stack Software Engineering Internship}
\addcontentsline{toc}{section}{Full Stack Software Engineering Internship - Summer 2024}
\subsection*{At a Glance}
\begin{itemize}
    \item \textbf{Salary:} \$43–57/hour
    \item \textbf{Location:} \textbf{Foster City, CA}
    \item \textbf{Duration:} May 28 to August 23
    \item \textbf{Type:} Internship, Full-time
\end{itemize}

\subsection*{Qualifications}
\begin{itemize}
    \item \textbf{Pursuing a Bachelor's or Master's in Computer Science or related field.}
    \item \textbf{Fluency with at least one modern JS framework: Vue, Angular, or React.}
    \item \textbf{Experience with TypeScript, Flow or JavaScript.}
    \item \textbf{Experience with HTML/CSS.}
\end{itemize}

\subsection*{About Zoox}
Information about Zoox's focus on innovation and its vision for the future of urban mobility.

\subsection*{Improvement Notes and Project Suggestions}
\textbf{Master a JS Framework:} Deep dive into Vue, Angular, or React.\\
\textbf{Project Idea:} Build a fleet management dashboard to simulate monitoring and interaction with autonomous vehicles.


\subsection*{Resume Tailoring and Project Strategy for Full Stack Software Engineering Internship}
\textbf{Resume Tips:}
\begin{itemize}
    \item Ensure your experience with React.js, TypeScript, and front-end development is prominently displayed.
    \item Detail relevant projects and emphasize your skills in JavaScript frameworks and backend development.
\end{itemize}


\newpage

\textbf{Project Idea:}
Create a fleet management dashboard utilizing React.js and TypeScript, incorporating backend technologies to simulate data management and vehicle tracking.


\input{jobs/Post_1/project.tex}